---
output: html_document
---
# Explore & Summarize Data: For Baseball


```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

# set up working directory
setwd("C:/Users/d023553/Documents/Business/SeminarsBooks/NanoDegree_DataSience/Lesson6/ProjectL6/Baseball/P6-Data-Visualization")

library(ggplot2)
library(dplyr)
library(GGally)
library(gridExtra)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
rw <- read.csv("baseball_data.csv")
```

Based on the insights I tested 2 apporaves Boxplot and scatter plot (see sketches)


--------

### Analysing and understand the dataset
```{r echo=TRUE, Analysis}
str(rw)     #Compactly Display the Structure of an Arbitrary R Object
summary(rw) #Object SUmmaries
help (bxp)
boxplot(count ~ names , data = avg)
```

Initial observations:


To first explore this data visually, I'll use the ggpair function and apply it to the data-set "rw". This will give me quick insights on the 5 variables. The intention here is to see a quick distribution of the values.


```{r echo=FALSE, Initial_Observations2}
# included the jpg since the processing time is too long
ggpairs(rw, columns = 2:6, title="Quick insights on dataset Baseball")
```
